### 2019-10-01 uiuc.tex
airports and typos

\subsubsection{Accessibility and Accomodation}
 Many hotels are located around downtown Champaign and the Eastern 
 side of campus, making transportation easy. Champaign-Urbana Mass Transit 
 (CU-MTD) is a reliable public transportation service that sees millions of 
 riders every year. CU-MTD charges an affordable rate of \$1 per ride, which 
 can be paid in cash or using the Token Transit app. Additionally, an all-day 
 pass can be bought on Saturdays and Sundays for \$2 from any bus operator or 
 from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and 
 rideshare services are also plentiful.
 Champaign's Willard Airport (CMI) is just 15 minutes from campus and has 
regular flights to and from Chicago O’Hare (ORD), Dallas/Fort Worth (DFW), and 
Charlotte (CLT). Finally, Peoria Charter is a popular bus service with several 
daily trips between the UIUC campus and the Chicagoland area.

>>>>

\subsubsection{Accessibility and Accomodation}
 Many hotels are located around downtown Champaign and the Eastern 
 side of campus, making transportation easy. Champaign-Urbana Mass Transit 
 (CU-MTD) is a reliable public transportation service that sees millions of 
 riders every year. CU-MTD charges an affordable rate of \$1 per ride, which 
 can be paid in cash or using the Token Transit app. Additionally, an all-day 
 pass can be bought on Saturdays and Sundays for \$2 from any bus operator or 
 from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and 
 rideshare services are also plentiful.
 Champaign's Willard Airport (CMI) is just 15 minutes from campus and has 
regular flights to and from Chicago O’Hare (ORD), Dallas/Fort Worth (DFW), and 
Charlotte (CLT).  Other nearby airports include Chicago (ORD and MDW),
Indianapolis (IND), and Bloomington (BMI). If attendees fly into these
airports, ground transportation to the Champaign area will be required. To this
end, Peoria Charter is a popular bus service with several 
daily trips between the UIUC campus and the Chicagoland area.
